---
title: "36-613: Data Visualization"
description: |
  Companion website for the MSP Data Visualization course offered in Fall 2022 Mini 1 and taught by Professor Ron Yurko.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```

## Course Objectives

TBA

## Lectures

Lecture slides are available below in html format, and the .Rmd files are linked from GitHub.

| Lecture | Topic                         | html                                                                               | Rmd                                                                                                              |
|-----------|-----------------------------------------|-----------|-----------|
| 1       | Intro and Grammar of Graphics | [`r icons::fontawesome$solid$laptop`](https://cmu-36613.netlify.app/slides/Lec1#1) | [`r icons::fontawesome$brands$github`](https://github.com/ryurko/DataViz-36613-Fall22/blob/main/slides/Lec1.Rmd) |

## R Demos

Additional `R` demos are available below in html format.

## Resources

### Data Visualization

-   Fundamentals of Data Visualization: <https://clauswilke.com/dataviz/index.html>

-   Data Visualization: A Practical Introduction: <https://socviz.co/index.html#preface>

### The tidyverse

-   Best resource for overall analysis in R using the tidyverse: <https://r4ds.had.co.nz/>

### `ggplot2`

-   `ggplot2` book: <https://ggplot2-book.org/>

-   The `ggplot2` cheatsheet: <https://www.maths.usyd.edu.au/u/UG/SM/STAT3022/r/current/Misc/data-visualization-2.1.pdf>

-   Creating custom themes: <https://themockup.blog/posts/2020-12-26-creating-and-using-custom-ggplot2-themes/>

-   R Graphics cookbook: <https://r-graphics.org/>

-   A guide to various scales: <https://ggplot2tor.com/scales>

### R Markdown

-   The definitive guide to R Markdown: <https://bookdown.org/yihui/rmarkdown/>

-   R Markdown reference guide: <https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf>

-   R Markdown cheat sheet: <https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf>

## Acknowledgments {.appendix}

This course website is made with the [distill package](https://rstudio.github.io/distill/). Thanks to [Meghan Hall](https://meghan.rbind.io/), [Alison Hill](https://rstudio-education.github.io/teaching-in-production/), and [Shamindra Shrotriya](https://www.shamindras.com/posts/2019-07-11-shrotriya2019distillpt1/) for their incredible examples and tutorials that helped in the process of making this site.

```{r, include=FALSE, results='asis'}
library(metathis)
meta() %>%
  meta_social(
    title = "CMU 36-613",
    description = "Course website for Data Visualization, by Ron Yurko",
    url = "https://cmu-36613.netlify.app/",
    image_alt = "CMU 36-613",
    og_type = "website",
    og_author = "Ron Yurko",
    twitter_card_type = "summary",
    twitter_creator = "@Stat_Ron"
  )
```
